---
output:
  html_document: default
  pdf_document: default
---
# Regression and model variation

This week I have revised the basics of **linear and multiple regression analysis**, and started to learn about how to both **perform** and **interpret** these analyses in R. It has been fun! I am also getting the hang of using RMarkdown, which is great. Here below you can see, . The main finding is that. :-)

# Starting data analysis

# STEP 1.Reading data.
```{r }
setwd("/Users/testitesti/Documents/GitHub/IODS-project/data/")
getwd()

learning2014 <- read.csv(file = "learning2014.csv")
```

# Demonstrating reading abilities of structure and dimensions
```{r }
str(learning2014)
head(learning2014)
dim(learning2014)
```
# STEP 2
# Creating a plot matrix
```{r }
p <- ggpairs(learning2014, mapping = aes(col = gender), lower = list(combo = wrap("facethist", bins = 20)))
```

# Drawing the plot
```{r }
p
```
# Choosing variables for multiple regression. Creating a regression model with multiple explanatory variables
```{r }
my_model2 <- lm(Points ~ Attitude + stra + surf, data = learning2014)
```

# print out a summary of the model
```{r }
summary(my_model2)
```
# Producing the diagnostic plot: residuals vs fitted values, normal QQ-plot and residuals vs leverage

```{r }
par(mfrow = c(2,2))
plot(my_model2, which = c(1,2,5))
```

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  
